---
title: "Introduction to RITANdata"
author: "Michael T. Zimmermann"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

RITAN is an R package intended for Rapid Integration of Term Annotation and Network resources. RITANdata is an R package containing data to support RITAN.

```{r load_data from package, echo=TRUE, results='hide'}
library(RITANdata)
```

# Pathways, Terms, and Genesets

The R object *geneset_list*
This version of RITAN is distributed with the following annotation resources:
```{r echo_geneset_list_names, echo=TRUE }
names(geneset_list)
```

Please cite each resource used in your analysis. If you use data from MSigDB, please register at [MSigDB](http://software.broadinstitute.org/gsea/msigdb/index.jsp). Doing so will help to ensure the future availability and extension of these valuable resources.

# Network Resources

The R object, *network_list*, contains `r length(network_list)` human network-biology resources. Additionally, RITAN leverages existing R packages to access data from HPRD, BioGRID, and STRING. Citation information for each resource can be accessed via attr():
```{r net_citation, echo=TRUE}
require(knitr)
kable( attr(network_list, 'network_data_sources') )
```


